### 2015-06-29 Projects/DelCo_2012/Report/DelCo_2012.tex
Delco_2012: update report, figures

Each structure had burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.74~m (9.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer. The hallway was 0.95~m (3.1~ft) wide and 5.4~m (17.6~ft) and the entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft). The ceiling height in the hallway and entry foyer was 2.4~m (8~ft).  The open door on north side from the exterior to the entry foyer was 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide.  The opening on the south face of the structure from the exterior to the burn room was 2.4~m (7.75~ft) high and 1.09~m (3.6~ft) wide. A dimensioned, plan view of the structure is included in Fig.~\ref{fig:Test_Structure_Floor_Plan}.

@@

The floor of the structure was a concrete pad.  The interior walls of the structure were framed with steel studs and track.  The studs were set to 0.40 m (16 in) centers.  The ceiling support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in) depth.  The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.125 in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in .  Tongue and grove, 18.3 mm (0.72 in) thick, oriented strand board was attached to the top of the TJIs.

The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.  The ceiling of the burn room was the exposed ``floor assembly".  The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room. The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.

Both structures were similar and were used to run comparative experiments on a given day.

@@

@@

The structures were instrumented for temperature, heat flux, and gas velocity measurements.  A schematic plan view of the instrumentation arrangement is show in ????

@@

Thermocouples:
Work through the Seebeck effect.  Two dissimilar metals are joined together with a weld bead.  Each metal generates a voltage, different from one another, when exposed to a thermal gradient.  This voltage difference increases with an increase in energy to the thermocouple and through a correlation, a corresponding temperature is found.

@@

Gas temperatures in the burn room were measured with bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5 mm (0.02 in) nominal diameter.  Thermocouple arrays were installed 2.0 m (6.7 ft) from both the east and the west walls of the burn room and 2.1 m (6.9 ft) from the south wall as shown in Figure ..  The vertical arrays had thermocouples located 0.03, 0.3, 0.61, 0.91, 1.22, 1.52, 1.83, 2.13 m below the bottom edge of the joist, where a ceiling would be installed.

Additional single thermocouples were installed in conjunction with the bi-directional probes at the exterior vents and in the hallway.  The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0 mm (0.04 in) nominal diameter. Just behind the bead, the thermocouple wire is protected with an 3.2 mm (0.125 in) diameter inconnel sheath.  
In the north doorway, there were seven thermocouples were located at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft) below the soffit along the vertical centerline of the doorway opening.  In the hallway, there were seven thermocouples positioned vertically at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft)   In the south window opening, there were four thermocouples are located 0.28 m (0.95 ft), 0.58 (1.90 ft), 0.84 m (2.85 ft), and 1.16 m (3.8 ft) below the soffit.

\subsection{Heat Flux}
\label{subsec:Heat_Flux}

Total Heat Flux:
Water cooled heat flux gauges measure both the convective and radiative heat transfer to the sensor.  Hot and cold side of a plate simulating the hot and cold side of a thermocouple.  The temperature gradient generates a voltage and through correlations, a total heat flux measurement is obtained.  The sensor is water cooled to ensure a thermal gradient remains and the sensor does not reach uniform temperature.  The sensor top is painted black to assist with radiation absorption.

Radiometer:
The radiometer is simply a total heat flux gauge with Zirconium plate atop the sensor preventing the device from recording any heat due to convective transfer.

@@

Total heat flux was measured with Schmidt-Boelter gauges.  Radiant heat flux was measured with Schmidt Boelter gauges with sapphire lens.  One of each was located near the thermocouple arrays in the burn room.  The gauges were pointed at the ceiling and positioned 0.15 m (6 in) above the floor.

@@

\subsection{Gas Velocity}
\label{subsec:Gas_Velocity}

Bi-directional Probes:
- Fire flow measurements are taken using these devices which have a high and low pressure side.  These flows then travel to a pressure transducer.  Through a simple conversion, the voltages are converted to pressure and finally a velocity based on the pressure and corresponding temperature measurements.

@@

Gas velocity was determined utilizing differential pressure transducers connected to bidirectional velocity probes[ ] in conjunction with a temperature measurement.  These probes were co-located with the sheathed thermocouples in the north doorway, the south window opening and the hallway.  The locations are shown in ??????

>>>>

Each structure had burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.74~m (9.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer. The hallway was 0.95~m (3.1~ft) wide and 5.4~m (17.6~ft) long and the entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft). The ceiling height in the hallway and entry foyer was 2.4~m (8~ft).  The open door on north side from the exterior to the entry foyer was 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide. The opening on the south face of the structure from the exterior to the burn room was 2.4~m (7.75~ft) high and 1.09~m (3.6~ft) wide. A dimensioned, plan view of the structure is included in Fig.~\ref{fig:Test_Structure_Floor_Plan}.

@@

The floor of the structure was the concrete pad. The interior walls of the structure were framed with steel studs and track.  The studs were set to 0.40~m (16~in) centers. The ceiling support was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in) depth. The TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.125~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web. Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was attached to the top of the TJIs.

The interior walls of the burn room were lined with 13~mm (0.5~in) thick cement board. The ceiling of the burn room was the exposed ``floor assembly". The walls of the hallway and entry foyer were composed of 16~mm (0.625~in) Type X gypsum room. The ceiling of the hallway and entry foyer was composed of two layers of 13~mm (0.5~in) thick cement board.

@@

The structures were instrumented for temperature, gas velocity, and heat flux measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm (0.04~in) nominal diameter. The thermocouple wire was protected with an 3.2~mm (0.125~n) diameter inconnel sheath. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to isolate radiative heat transfer.

@@

  A schematic plan view of the instrumentation arrangement is show in ????

@@

@@

Thermocouple arrays were installed 2.0 m (6.7 ft) from both the east and the west walls of the burn room and 2.1 m (6.9 ft) from the south wall as shown in Figure ..  The vertical arrays had thermocouples located 0.03, 0.3, 0.61, 0.91, 1.22, 1.52, 1.83, 2.13 m below the bottom edge of the joist, where a ceiling would be installed.

In the north doorway, there were seven thermocouples were located at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft) below the soffit along the vertical centerline of the doorway opening.  In the hallway, there were seven thermocouples positioned vertically at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft)   In the south window opening, there were four thermocouples are located 0.28 m (0.95 ft), 0.58 (1.90 ft), 0.84 m (2.85 ft), and 1.16 m (3.8 ft) below the soffit.

@@

@@

@@
